SAT Competition 2020\tnoteref{title}

### 2021-01-25 paper/main.tex
conclusion

All winning solvers of the Main track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul runs to reconfigure weights in their branching heuristics.

From the results in the Parallel track, we can learn that it is still hard to scale from $32$ to $64$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel Cloud track, we could learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated architecture.

\todo{Should we have a discussion (maybe in later sections)
about the future of the portfolio solver rule
concerning the point raised by Mate Soos (in emails)?}

>>>>

All winning solvers of the \emph{Main} track periodically schedule runs of an SLS solver and import statistical information generated in unsuccessul SLS runs to reconfigure weights in their branching heuristics.

As can be seen in the \emph{Parallel} track, it is hard to scale SAT solving beyond $32$ threads, as in some occassions the $32$ threaded version of the same solver outperformed its $64$ threaded counterpart. 
However, from the winner in the massively parallel \emph{Cloud} track, we can learn that classic all-to-all clause-sharing can be outperformed by a more sophisticated clause-sharing architecture.

It is hard to integrate and test sophisticated state-of-the-art methods in an incremental SAT solver and thus solvers usually disable parts of their features in the incremental use-case. 
The winner of the \emph{Incremental Library} track showed that it is worth integrating full solver functionality in the incremental use-case.

\subsection*{Future Competitions}

The \emph{Portfolio rule} has been established to prohibit participation of pure solver portfolio and to stimulate development of new code-bases. This rule was challenged in this competition, as it can be hurtful to cooperation in the community when solver authors use the work of other researchers as fully integrated sub-systems in their own code-base.

Many prominent applications of SAT use an \emph{incremental} SAT solver in their backend. 
The emergence of new fuzzing tools for incremental SAT solvers based on IPASIR can help researchers with also integrating and testing their methods in the incremental use-case.\footnote{\url{https://github.com/fkutzner/IncrementalMonkey}}
